\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-10-02 chapters/bci.tex
Comments Marc

\todo{comments liesel paradigms})
\todo{spellcheck}
\todo{are all acronyms defined}
\todo{fix all latex warnings to make sure no refs are missing (or grep on that
specific warning)}
\todo{uniform ref or autoref}
\todo{don't capitalize figure, table, algorithm,...}
\todo{define short captions for tables and figures}
\todo{fix lacheck/chktex notifications}
\todo{use terminology individuals with severe
speech and physical impairments (SSPI), avoid phrasing 'suffering from'}
\todohsm{more subtitles}
\todofc{double check statements about what has been published 'for the sake of clarity, the introduction has been mofed to"}
\todofc{chapters should look more like full papers}

@@

\fullpagefigct{%
  \includegraphics[width=\textwidth]{figures/bci/bci_loop.pdf}
}{%
  The \ac{bci} loop.
  The user interacts with the \ac{bci} via a specific paradigm, in this case involving
  visual stimulation.
  Electrical neural signals are recorded, and neurophysiological features
  related to the paradigm are extracted. Using machine learning, a decision can
  then be made based on these features, which can be presented back to the user.
  In a closed-loop \ac{bci}, this feedback allows the user to adapt to the \ac{bci}.
}{%
  fig:bci/loop
}

@@

\fullpagefig{%
  \includegraphics[width=\textwidth]{figures/bci/recording_modalities.pdf}
}{%
	Different electrophysiology recording modalities and \\
	their respective position in a cross-section of the skull. \\
	There is a trade-off between invasiveness and  \\
	spatial resolution.
}{%
  fig:bci/recording
}

@@

\fullpagefig{%
  \input{figures/bci/paradigms.tikz.tex}
}{%
  A \ac{bci} paradigm defines which brain activity will be used for control.
  They can be categorized in active, reactive and passive
  paradigms, depending on their reliance on external stimulation and active
  participation required from the user.
  Adapted from~\textcite{Muehl2014}.
}{%
  fig:bci/paradigms
}
\todo{check permissions}
\todo{above Zander and Kothe was mentioned.}

>>>>

\todo{comments liesel paradigms})
\todo{spellcheck}
\todo{are all acronyms defined}
\todo{fix all latex warnings to make sure no refs are missing (or grep on that
specific warning)}
\todo{uniform ref or autoref}
\todo{don't capitalize figure, table, algorithm,...}
\todo{define short captions for tables and figures}
\todo{fix lacheck/chktex notifications}
\todo{use terminology individuals with severe
speech and physical impairments (SSPI), avoid phrasing 'suffering from'}
\todohsm{more subtitles}
\todofc{double check statements about what has been published 'for the sake of clarity, the introduction has been mofed to"}
\todofc{chapters should look more like full papers}
\todo{uniform vsa condition vsa setting}
\todo{acronyms written in full every new chapter and in captions}

@@

\fullpagefigct{%
  \includegraphics[width=\textwidth]{figures/bci/bci_loop.pdf}
}{%
  The \ac{bci} loop.
}{%
  The \ac{bci} loop.
  The user interacts with the \ac{bci} via a specific paradigm, in this case involving
  visual stimulation.
  Electrical neural signals are recorded, and neurophysiological features
  related to the paradigm are extracted. Using machine learning, a decision can
  then be made based on these features, which can be presented back to the user.
  In a closed-loop \ac{bci}, this feedback allows the user to adapt to the \ac{bci}.
}{%
  fig:bci/loop
}

@@

\fullpagefig{%
  \includegraphics[width=\textwidth]{figures/bci/recording_modalities.pdf}
}{%
  Various electrophysiology recording technologies.
}{%
	Various electrophysiology recording technologies and \\
	their respective position in a cross-section of the skull. \\
	There is a trade-off between invasiveness and  \\
	spatial resolution.
}{%
  fig:bci/recording
}

@@

\fullpagefig{%
  \input{figures/bci/paradigms.tikz.tex}
}{%
  Overview of \ac{bci} paradigms.
}{%
  A \ac{bci} paradigm defines which brain activity will be used for control.
  They can be categorized in active, reactive and passive
  paradigms, depending on their reliance on external stimulation and active
  participation required from the user.
  Adapted from~\textcite{Muehl2014}.
}{%
  fig:bci/paradigms
}
\todo{check permissions}
\todo{above Zander and Kothe was mentioned.}
